PhotoD with LSST: stellar photometric distances out to the edge of the Galaxy

### 2024-01-08 paper/paper.tex
abstract edits

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
As demonstrated with SDSS, Pan-STARRS and most recently with Gaia data, broad-band near-UV to near-IR photometry can be used 
to estimate distances, metallicity and the interstellar dust extinction along the line of sight for stars in the Galaxy. Anticipating
photometric catalogs with tens of billions of stars from Rubin's Legacy Survey of Space and Time (LSST), we present a fully Bayesian procedure 
and pipeline that build on previous work and can handle LSST-sized datasets. Likelihood computations utilize MIST/Dartmouth isochrones
and priors are derived from TRILEGAL-based simulated LSST catalogs from Dal Tio et al. (2022). The computation speed is about 10 mas per
star for both optimized grid search and MCMC methods; we show in a companion paper by Mrakov\v{c}i\'{c} et al. how to utilize neural
networks to accelerate this performance by an order of magnitude).  We validate our pipeline, named
PhotoD (in analogy with photo-z, photometric redshifts of galaxies) using both simulated catalogs, and SDSS, DECam, and Gaia data. 
We intend to make LSST-based value-added PhotoD catalogs publicly
available via Rubin Science Platform with every LSST Data Release. 
\end{abstract}

@@

	paper/Makefile
	paper/aastex.cls
	paper/aastex63.cls
	paper/apj.bst
	paper/appendix.tex
	paper/deluxetable.sty
	paper/lsst.sty
	paper/methodologyZI.tex
	paper/paper.bib
	paper/paper.pdf
	paper/paper.tex
	paper/results.tex

        plots/2Dmap.png
	plots/2Dmap_Stripe82_MrSDSS_MrGaia.png
	plots/2Dmap_Stripe82_MrSDSS_MrGaia_piSNR20.png
	plots/2Dmap_Stripe82_MrdMr_piSNR20.png
	plots/QrCornerPlot.png
	plots/bayesPanels.png
	plots/cornerPlot3.png
	plots/margPosteriors.png
	plots/margPosteriors3D.png
	plots/qpB_Ar.png
	plots/qpB_FeH.png
	plots/qpB_Mr.png
	plots/qpB_chiTest4_3D_Ar.png
	plots/qpB_chiTest4_3D_FeH.png
	plots/qpB_chiTest4_3D_Mr.png
	plots/qpB_chiTest4_FeH.png
	plots/qpB_chiTest4_Mr.png
	plots/qpBcmd.png
	plots/qpBcmd_chiTest4_3D_Ar.png
	plots/qpBcmd_chiTest4_3D_FeH.png
	plots/qpBcmd_chiTest4_3D_Mr.png
	plots/qpBcmd_chiTest4_FeH.png
	plots/qpBcmd_chiTest4_Mr.png
	plots/qpBmeans_chiTest4_.png
	plots/qpBmeans_chiTest4_3D.png

>>>>

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}
As demonstrated with SDSS, Pan-STARRS and most recently with Gaia data, broad-band near-UV to near-IR stellar photometry can be used 
to estimate distance, metallicity and interstellar dust extinction along the line of sight for stars in the Galaxy. Anticipating
photometric catalogs with tens of billions of stars from Rubin's Legacy Survey of Space and Time (LSST), we present a Bayesian procedure 
and pipeline that build on previous work and can handle LSST-sized datasets. Likelihood computations utilize MIST/Dartmouth isochrones
and priors are derived from TRILEGAL-based simulated LSST catalogs from Dal Tio et al. (2022). The computation speed is about 10 milliseconds per
star on a single core for both optimized grid search and MCMC methods; we show in a companion paper by Mrakov\v{c}i\'{c} et al. how to utilize neural
networks to accelerate this performance by an order of magnitude.  We validate our pipeline, named
PhotoD (in analogy with photo-z, photometric redshifts of galaxies) using both simulated catalogs, and SDSS, DECam and Gaia data. 
We intend to make LSST-based value-added PhotoD catalogs publicly
available via Rubin Science Platform with every LSST Data Release. 
\end{abstract}

@@
